A Review on Multi-Label Learning Algorithms

### 2018-01-14 Paper/Presentation/mll_review.tex
update presentation, check the last 2 algorithms

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

\documentclass{beamer}
\setbeamercovered{transparent}
\setbeamercolor{local structure}{fg=black}
\setbeamertemplate{caption}{\raggedright\insertcaption\par}
\usefonttheme[onlymath]{serif}

@@

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{caption}
\captionsetup{font=scriptsize,labelfont=scriptsize}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

@@

\author[Sissy Themeli, Nikiforos Pittaras]{Min-Ling Zhang and Zhi-Hua Zhou} % Your name
\institute[DI-UOA] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
	IEEE TRANSACTIONS ON KNOWLEDGE AND DATA ENGINEERING\\ % Your institution for the title page
	\medskip
}
\date{\today} % Date, can be changed to a custom date

@@

%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------

%------------------------------------------------
\section{Introduction} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
\subsection{Problem Definition}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Single-label supervised learning
\begin{itemize}
	\item Applied to classification
	\item Supervised: Dataset $\{ (x_i, y_i)\}, i = 1, \dots N, x \in X, y \in Y$
	\item Goal is to learn a model $f: X \rightarrow Y$
\end{itemize}

@@

\end{itemize}
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
	\item First-order approach algorithm, that adopts decision tree techniques
	\item ML entropy is used to
build the decision tree recursively
	\item ML dataset $T$ is divided based on a splitting value $\theta$ ($T^-$ \& $T^+$)
	\item Starting from the root, ML-DT identifies the feature and the splitting value which
maximizes the information gain and creates the two child nodes
	\item ML-DT assumes independence among labels and computes the ML
entropy in a decomposable way
	\item Any test instance allocated in a leaf node is associated with the most frequent label $y$ present in that node
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item High efficiency
	\item Improvement: pruning strategy  or ensemble learning techniques
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item Second-order approach algorithm, that adopts maximum margin strategy 
	\item $q$ linear classifiers, optimized to minimize the empirical
ranking loss and enabled to handle nonlinear cases with kernel tricks 
	\item $W = {(w_j , b_j ) | 1 ≤ j ≤ q}$,where $w_j \in \mathbb{R}^d$ and
$b_j \in \mathbb{R}$ are the weight vector and bias
	\item Rank-SVM defines the learning system's
margin on ($x_i$ , $Y_i$), considering its ranking ability on the example’s relevant/irrelevant labels
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
	\item 
	\item 
	\item 
	\item 
\end{itemize}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------

\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
	\item 
	\item 
	\item 
	\item 
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
	\item 
\end{itemize}
\end{frame}

%------------------------------------------------
\section{The end}
\begin{frame}
\Huge{\centerline{Thank you}}
\end{frame}
%------------------------------------------------
\end{document}

>>>>

%-------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%-------------------------------------------------------------------------------------
\documentclass{beamer}
\setbeamercovered{transparent}
\setbeamercolor{local structure}{fg=black}
\setbeamertemplate{caption}{\raggedright\insertcaption\par}
\usefonttheme[onlymath]{serif}

@@

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{caption}
\captionsetup{font=scriptsize,labelfont=scriptsize}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}                                                                                                    
%-------------------------------------------------------------------------------------
%	TITLE PAGE
%-------------------------------------------------------------------------------------

@@

\author[Sissy Themeli, Nikiforos Pittaras]{Min-Ling Zhang and Zhi-Hua Zhou} % Your name
\institute[DI-UOA] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
	IEEE Transactions On Knowledge And Data Engineering\\ % Your institution for the title page
	\medskip
}
\date{\today} % Date, can be changed to a custom date

@@

%-------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%-------------------------------------------------------------------------------------

\section{Introduction} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
\subsection{Problem Definition}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Single-label supervised learning
\begin{itemize}
	\item Applied to classification
	\item Supervised: Dataset $\{ (x_i, y_i)\}, i = 1, \dots N, x \in X, y \in Y$
	\item Goal is to learn a model $f: X \rightarrow Y$
\end{itemize}

@@

\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
	\item First-order approach algorithm, that adopts decision tree techniques
	\item ML entropy is used to
build the decision tree recursively
	\item ML dataset $T$ is divided based on a splitting value $\theta$ ($T^-$ \& $T^+$)
	\item Starting from the root, ML-DT identifies the feature and the splitting value which
maximizes the information gain and creates the two child nodes
	\item ML-DT assumes independence among labels and computes the ML
entropy in a decomposable way
	\item Any test instance allocated in a leaf node is associated with the most frequent label $y$ present in that node
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item High efficiency
	\item Improvement: pruning strategy  or ensemble learning techniques
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item Second-order approach algorithm, that adopts maximum margin strategy 
	\item $q$ linear classifiers, optimized to minimize the empirical
ranking loss and enabled to handle nonlinear cases with kernel tricks 
	\item $W = {(w_j , b_j ) | 1 ≤ j ≤ q}$,where $w_j \in \mathbb{R}^d$ and
$b_j \in \mathbb{R}$ are the weight vector and bias
	\item Rank-SVM defines the learning system's
margin on ($x_i$ , $Y_i$), considering its ranking ability on the example’s relevant/irrelevant labels

TODO!!!
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Benefits from kernels to handle non-linear classification problems
	\item Multiple kernel learning techniques can be
employed to learn from multi-label data
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
	\item Second-order approach algorithm, that adapts maximum entropy
principle \item Correlations
among labels are encoded as constraints that the resulting
	distribution must satisfy
	\item 
	\item 
	\item 
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item More general than Rank-SVM, that only considers relevant-irrelevant label pairs
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Summary}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.45]{images/summary.png}
		\caption{Summary of Representative Multi-Label Learning Algorithms}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
	\item Multi-instance learning
	\begin{itemize}
		\item Each example described by a bag of instances while associated with a single/binary label
		\item Models the object’s ambiguities in input space
	\end{itemize}
	\item Ordinal classification
	\begin{itemize}
		\item Natural ordering of class labels and their relevance
		\item Vague (ordinal) instead
of definite judgment on the label relevance
	\end{itemize}
	\item Multi-task learning
	\begin{itemize}
		\item Multiple tasks are trained in parallel, usually small number of tasks
		\item Training
information of related tasks used as an inductive bias to improve the generalization performance of other tasks
		\item Tasks
can be in the same or different feature space
	\end{itemize}
	\item Data streams classification
	\begin{itemize}
		\item Real-world objects are generated online and processed in a real-time manner
	\end{itemize}
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Conclusion}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Online resources}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.47]{images/online.png}
		\caption{Online Resources for Multi-Label Learning}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
Summary
\begin{itemize}
	\item ML learning problem definition 
	\item ML learning representative algorithms
	\item Related learning settings
\end{itemize}

Open research problems
\begin{itemize}
	\item Full understanding and appropriate usage of label correlations (might be asymetric or local)
	\item Conduct thorough experimental studies to
get insights on the pros and cons of different multi-label
learning algorithms
\end{itemize}
\end{frame}

%------------------------------------------------
\section{The end}
\begin{frame}
\Huge{\centerline{Thank you}}
\Huge{\centerline{Questions?}}
\end{frame}
%------------------------------------------------
\end{document}
